%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\usepackage{comment}

\setlength{\textwidth}{5.29in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Hasan Saad} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{{\bf Address:\ } Kerchof Hall, 141 Cabell Dr, Charlottesville, VA 22903}
\moveleft1.27\hoffset\centerline{{\bf Email:\ } \href{mailto:hs7gy@virginia.edu}{hs7gy@virginia.edu}}
\moveleft1.53\hoffset\centerline{{\bf Personal Website:\ } \href{hasansaad2.github.io}{hasansaad2.github.io}}
\moveleft1.65\hoffset\centerline{{\bf Phone Number:\ } 434-227-7173}


%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 \begin{comment}
\section{OBJECTIVE}  

Motivated college student with special interests in Mechanical Engineering and experience with food service, retail, and personal services. Proven track record of excellent performance and advancement.

\end{comment}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

\begin{itemize}
    \item University of Virginia, Ph.D. Mathematics (August 2022 - May 2024), M.S. Mathematics (December 2022)
    \item American University of Beirut, M.S. Mathematics (January 2018 - December 2020)\footnote{I didn't complete my study for a Master's degree at AUB since I was accepted to UVA before my final semester.}
    \item Lebanese University, B.S. Mathematics (2018)
\end{itemize}

\section{PUBLICATIONS}
\begin{itemize}
    \item \emph{Distribution of values of Gaussian hypergeometric functions}, (Co-authors: Ken Ono and Neelam Saikia).\newline
    Pure and Applied Mathematics Quarterly, Special Issue for Don Zagier’s 70th birthday,  {\bf 19}, no. 1 (2023), 371-407.

    \item \emph{Explicit Sato--Tate type distribution for a family of K3 surfaces}.\newline
    Forum Mathematicum {\bf 35}, no. 4 1105-1132. 2023.

    \item \emph{Some Eichler--Selberg Trace Formulas}, (Co-author: Ken Ono).\newline
    The Hardy Ramanujan Journal 45, 94-107. 2022.

    \item \emph{Matrix points on special varieties over finite fields}, (Co-authors: Yifeng Huang and Ken Ono).\newline
    Contemporary Mathematics, American Mathematical Society, accepted
for publication.
\end{itemize}

\section{CONFERENCE PRESENTATIONS}

\begin{itemize}
    \item July 2022 \emph{ Distribution of values of Gaussian hypergeometric functions},\newline
    HKU Number Theory Days 2022 (Zoom).
    \item  January 2023 \emph{Explicit Sato-Tate distributions for hypergeometric varieties}, \newline
    AMS Special Session on Modular Forms, Hypergeometric Functions, Character Sums and Galois Representations I, Joint Math Meetings, Boston.
    \item April 2023 \emph{ Counting matrix points on hypergeometric varieties over finite fields},\newline
     Special Session on Hypergeometric Functions, q-series and Generalizations, 2023 AMS Spring Virtual Eastern Sectional Meeting
     \item May 2023, \emph{Determining point distributions on hypergeometric varieties}\newline
     35th Automorphic Forms Workshop, Louisiana State University.
\end{itemize}

\section{TEACHING}

\begin{itemize}
    \item Spring 2019, Instructor for Math 201 (\textbf{Calculus and Analytic Geometry III}), American University of Beirut (AUB)
    \item Summer 2021 Session I, TA for Math 1310 (\textbf{Calculus I}), University of Virginia (UVA)
    \item Summer 2021 Session II, TA for Math 1310 (\textbf{Calculus I}), UVA
    \item Fall 2021, Instructor for MATH 1210 (\textbf{A Survey of Calculus I}), UVA
    \item Spring 2022, Instructor for MATH 1210 (\textbf{A Survey of Calculus I}), UVA
    \item Fall 2023, Instructor for Math 1320 (\textbf{Calculus II}), UVA

\end{itemize}

\end{resume}
\end{document}